---
title: "Ratio to standard"
output:
  html_document:
    df_print: paged
---

Checking SNICSer ratio to std results against MR's results from Fudger. Using CFAMS070821 and CFAMS103021.

```{r}
library(tidyverse)
library(readxl)
```

Read data

```{r}
fudger0708 <- read_xlsx("data/CFAMS070821 Norm Results.xlsx", skip = 5) %>% 
  filter(!Rpts == 0) %>% 
  mutate(wheel = "CFAMS070821")
fudger1030 <- read_xlsx("data/CFAMS1030821 Norm Results.xlsx", skip = 5) %>% 
  filter(!Rpts == 0) %>% 
  mutate(wheel = "CFAMS103021")

fudger <- bind_rows(fudger0708, fudger1030)
# fudger <- map_dfr(list.files(path = "data", 
#                               pattern = "Results.xlsx",
#                               full.names = TRUE), read_xlsx, .id = "wheel", skip = 5)

snicser_files <- list.files(path = "data", 
                              pattern = "TargetTable.xls",
                              full.names = TRUE)

snicser <- snicser_files %>% 
  set_names() %>% 
  map_dfr(read_tsv, .id = "wheel") %>% 
  mutate(wheel = word(basename(wheel), sep = "_"))

combined <- snicser %>% 
  select(wheel, Pos, SampleName, Typ, N, DelC13, NormRat) %>% 
  left_join(select(fudger, wheel, Pos., fRpts = Rpts, fdel13C = `del13C to STD`, fnormrat = `Ratio to STD`), by = c("wheel" = "wheel", "Pos" = "Pos.")) %>% 
  filter(!is.na(fnormrat)) %>% 
  mutate(diff = fnormrat - NormRat)
```

There are some oddnesses in the differences. The slope of low ratio stuff is interesting. Is there a blank correction happening somewhere?

```{r}
ggplot(combined, aes(NormRat, diff, color = DelC13)) +
  geom_point()
```

Same for 10/30 wheel. Snicser run with 14/12 set to 1, 13/12 set to .9822. Bracket average, allow self-norm.

 
 Looking at the sample with the largest difference. Was this defined to be zero and used as a blank?
 
```{r}
combined %>% 
  arrange(diff) %>% 
  head()
```

Distribution of differences in standards seems to be random.

```{r}
combined %>% 
  filter(Typ == "S") %>% 
  ggplot(aes(NormRat, diff)) +
    geom_point()
  
```

```{r}
ggplot(combined, aes(DelC13, fdel13C - DelC13, color = wheel)) +
  geom_point()
```
```{r}
combined %>% 
  select(wheel, Pos, NormRat, snicser = DelC13, fudger = fdel13C) %>% 
  pivot_longer(cols = c(snicser, fudger), values_to = "d13C", names_to = "analysis") %>% 
  ggplot(aes(Pos, d13C, color = analysis)) +
  geom_point() +
  facet_wrap(~wheel)
```


```{r}
ggplot(combined, aes(DelC13, diff, color = fdel13C)) +
  geom_point()
```