---
title: "SNICSer Test"
output: html_notebook
---

Bits of code to test new versions of snicser against previous results

Load Libraries

```{r}
packages <- c("tidyverse", "amstools", "odbc")
lapply(packages, library, character.only = TRUE)

#con <- conNOSAMS()
```


Read orginal data. SNICSer version 2.95.

```{r}
# origdf <- getWheel("USAMS030520", TRUE)
# View(origdf)
# write_csv(origdf, "USAMS030520_orig.csv")
origdf <- read_csv("USAMS030520_orig.csv")
```

Read test data. Need to wipe old wheel and perform new analyst for 1st and second.

This will clear USAMS030520 from snics_raw_test and snics_results test

```{r}
# query <- dbSendQuery(con, "DELETE FROM snics_raw_test WHERE wheel = 'USAMS030520'")
# dbClearResult(query)
# query <- dbSendQuery(con, "DELETE FROM snics_results_test WHERE wheel = 'USAMS030520'")
# query
# dbClearResult(query)
```

Set 1st analyst to allow me to be second

```{r}
# query <- dbSendQuery(con, "UPDATE snics_raw_test SET analyst = 'brettl' WHERE wheel = 'USAMS030520'")
# dbClearResult(query)
# query <- dbSendQuery(con, "UPDATE snics_raw_test SET analyst = 'test' WHERE wheel = 'USAMS030520'")
# dbClearResult(query)
# query <- dbSendQuery(con, "UPDATE snics_results_test SET analyst1 = 'test' WHERE wheel = 'USAMS030520'")
# dbClearResult(query)
```

```{r}
# testdf <- getWheel("USAMS030520", TRUE)
# View(testdf)
# write_csv(testdf, "USAMS030520_test.csv")
testdf <- read_csv("USAMS030520_test.csv")
```

Are the blank corrected Fm's the same?

```{r}
origdf$test <- "orig"
testdf$test <- "test"
df <- rbind(origdf, testdf)

# names(df)
```

# Check that 1st and 2nd are the same

```{r}
df %>% 
  select(wheel_pos, fm_mb_corr, fm_mb_corr_2) %>% 
  mutate(same = near(fm_mb_corr, fm_mb_corr_2)) %>% 
  filter(same = FALSE)
```

# Check that old and new are the same for 1st

```{r}
df %>% 
  select(wheel_pos, test, fm_mb_corr) %>% 
pivot_wider(names_from = test, values_from = fm_mb_corr ) %>% 
  mutate(same = near(orig, test)) %>% 
  filter(same = FALSE)
```

# Check that old and new are the same for 2nd

```{r}
df %>% 
  select(wheel_pos, test, fm_mb_corr_2) %>% 
pivot_wider(names_from = test, values_from = fm_mb_corr_2 ) %>% 
  mutate(same = near(orig, test)) %>% 
  filter(same = FALSE)
```
